---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

author_note: >
  Complete departmental affiliations for each author (note the indentation, if you start a new paragraph).

  Enter author note here.

abstract: >
  Enter abstract here (note the indentation, if you start a new paragraph).
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["bibliography.bib"]

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no

lang              : "english"
class             : "man"
output            : papaja::apa6_word 
---

```{r include = FALSE}
library("papaja")
```

There is a lot of important literature to cite [@button_power_2013;@ioannidis_why_2005]. @sterne_recommendations_2011 have important things to say.

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

# Results

The mean length is `r mean(iris$Sepal.Length)`. Table \@ref(tab:myTable) shows some interesting results. Figure \@ref(fig:myFigure) shows an interesting plot.

```{r myTable, results = "asis"}
  knitr::kable(
  head(mtcars[, 1:8], 10), booktabs = TRUE,
  caption = 'A table of the first 10 rows of the mtcars data.'
  )
```

```{r myFigure, fig.height=3, fig.cap="This is a figure."}
  library(tidyverse)
  ggplot(iris, aes(Sepal.Length)) + 
    geom_histogram() + 
    facet_grid(. ~ Species) +
    theme_bw()
```


# Discussion


\newpage

# References
```{r create_r-references, eval=FALSE}
r_refs(file = "bibliography.bib")
```

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
