---
title: "IEDSFB Week 5"
author: "Your Name Here"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
  library(knitr)
  knitr::opts_chunk$set(echo = TRUE)
  opts_knit$set(root.dir=normalizePath('../'))
  library(tidyverse)
```

# Tidy data

Start by loading the `tidyverse` package.

```{r packages}
# load tidyverse

```

Here are some chunks for running tutorial examples:

```{r table4a}

```


```{r table4b}

```


```{r table2}

```


```{r table3}

```


```{r table5}

```


```{r stocks}

```


# Disclosure example

## Download data to your machine

If you completed the Week 4 tutorial, you should already have the data file you need for today. If not, run the following chunk. Notice that the chunk is set to `eval=FALSE` so that R will not download the file over and over again when you knit.

```{r download, eval=FALSE, warning=FALSE, message=FALSE}
  download.file("https://www.dropbox.com/s/g8ufwky4npt26as/r2d2-w04.csv?dl=1", 
                destfile = "input/r2d2-w04.csv")
```

## Import data into your environment

Write a line of code to import this file into your environment. 

```{r loadCSV}
# hint
# dat <- 

```

## Tidy!

```{r mean}

```


```{r mean_pipe}

```


```{r coded}

```


```{r indicator}

```


```{r mean_by}

```


```{r names}

```


```{r all_vars}

```


```{r gather}

```


```{r spread}

```


```{r nicer}

```






