---
title: "IEDSFB Week 4"
author: "Your Name Here"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
  library(knitr)
  knitr::opts_chunk$set(echo = TRUE)
  opts_knit$set(root.dir=normalizePath('../'))
  library(tidyverse)
```

# Download data to your machine

Run the following code chunk to get the data for today. Notice that the chunk is set to `eval=FALSE` so that R will not download the file over and over again when you knit.

```{r download, eval=FALSE, warning=FALSE, message=FALSE}
  download.file("https://www.dropbox.com/s/g8ufwky4npt26as/r2d2-w04.csv?dl=1", 
                destfile = "input/r2d2-w04.csv")
```

# Import data into your environment

Write a line of code to import this file into your environment. 

```{r loadCSV}
# hint
# dat <- 


```

# Take a quick glimpse

Load the `tidyverse` package and take a quick glimpse at the data. Try `glimpse()`, then turn `dat` into a tibble. 

```{r glimpse}

```

# Filter

How many observations do we have of female caregivers (`p.female.r1`) and female children (`c.female.r1`)?

```{r filter}

```

# Arrange

Try arranging by child age and then gender. Note how the order matters.

```{r arrange}

```

# Select

Get all of the knows variables.

```{r select}

```

# Mutate

Add a step to mutate that creates a variable in `temp` called `ageDiff50` that equals `1` if the age difference between kids and caregivers is at least 50 years.

```{r mutate}

```

# Pipe

Create a pipe that calculates the mean age difference between parents and kids by parent gender.

```{r pipes}

```

# Construct New Disclosure Variables

```{r fullDisclosure}

```

```{r ageFull}

```

```{r allTogetherNow}

```

# Run a script that is best to ignore for now

```{r dontworry}
  source("https://raw.githubusercontent.com/ericpgreen/IEatDataScience/master/scripts/csum.R")
```

## Build the plot here!

```{r plot}
dat %>%
  select(doesKnow15.r1, doesKnow19.r1,
         doesKnow23.r1, doesKnow27.r1,
         ageFull, c.age.r1) %>%
  melt(., id="c.age.r1") %>%
  group_by(variable, value) %>%
  summarise(count=n()) %>% # summarise first to get count by age
  group_by(variable) %>% #
  mutate(all=sum(count),
         count=as.numeric(count), # this is so that it goes in numeric order
         value=as.numeric(value)) %>%
  filter(!is.na(value)) %>%
  arrange(variable, value) %>%
  group_by(variable) %>%
  mutate(csum=cumsum(count),
         pct=(csum/all)*100) %>%
  mutate(label=ifelse(variable=="doesKnow15.r1", "Chronic Condition",
                      ifelse(variable=="doesKnow19.r1", "HIV Status",
                      ifelse(variable=="doesKnow23.r1", "How Infected",
                      ifelse(variable=="doesKnow27.r1", "Can Spread",
                      ifelse(variable=="ageFull", "Full Disclosure", 
                             "WTF")))))
         ) %>%
  data.frame(.) %>% # before you can rbind, you need to data.frame(.) it 
  rbind(., zeroDat) %>% 
  mutate(label=ifelse(value==15, label, "")) %>%
  mutate(hiv=ifelse(variable=="doesKnow19.r1", "hiv", "not")) %>%
  
  # start plot, wrap it in braces 
  {
    ggplot(., aes(x=as.factor(value), y=as.numeric(pct), 
                  color=variable, group=variable, label=label, 
                  linetype=variable, size=hiv)) +
      geom_line() +
      scale_size_manual(values=c(2,1)) +
      ylim(0,100) +
      labs(x="Age", y="Percent (%)") +
      theme_minimal() +
      geom_hline(yintercept=50, linetype="dotted") +
      theme(legend.title=element_blank()) +
      geom_text(data=filter(., value==15), 
                aes(x=as.factor(value), y=as.numeric(pct), label=label),
                vjust=c(rep(-1, 4), 4), hjust=1, size=4) +
      scale_color_manual(values=c("black", rep("black", 4))) +
      scale_linetype_manual(values=c("dashed", "solid", "solid",
                                     "solid", "solid"), name="") +
      guides(color=FALSE) +
      guides(linetype=FALSE) +
      guides(size=FALSE) +
      theme(panel.grid.major=element_blank(),
            panel.grid.minor=element_blank()) +
      theme(legend.position = "bottom")
  }
```

